---
title: "Spatial_LifeHistory"
output: html_document
Date: 2020.Mar.4
editor_options: 
  chunk_output_type: inline
---

# Note March 06
1. To identify index for intra-population spatial overlap
2. What is the hypothesis?
3. Other factors that influence intra-population spatial overlap (i.e. habitat heterogeneity, availability)


# Procedure:
1. To quantify the degree of ontogenetic niche shift
2. To link it with life history traits

# Reference list (online)

## Spatial distribution
https://onlinelibrary.wiley.com/doi/full/10.1111/ele.13360
https://www.nature.com/articles/s41598-019-53998-2
http://janohlberger.com/Homepage/download/cline-nature-ee-2019%20(1).pdf

## Ontogenetic niche shift
https://link.springer.com/article/10.1007/s10021-013-9645-4  

## Age structure model in dispersive/residence contingent
Kerr 2010 https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/08-1382.1

# R package "rfishbase"
```{r}
library("rfishbase")
library("dplyr")
fish <- c("Oreochromis niloticus", "Salmo trutta")
fish<-validate_names(c("Oreochromis niloticus", "Salmo trutta"))
fish
fish <- species_list(Genus = "Labroides")
fish
trout <- common_to_sci("trout")
trout
species(trout$Species)
dat <- species(trout$Species, fields=c("Species", "PriceCateg", "Vulnerability"))
dat
list_fields("Resilience")
stocks(trout$Species, fields=c("Species", "Resilience", "StockDefs"))

```



# Ideas
Differences in distribution between species depends on 
1. Ontogenetic-specific life history traits:
relative swimming behavior, changes in diet, 
*maximum body length* may correlates with all the above traits.

2. Environment:
landscape structure

3. Food availability

# North Sea species spatial autocorrelation
```{r}

```





