---
title: "Spatial_LifeHistory"
output: html_document
Date: 2020.Mar.4
editor_options: 
  chunk_output_type: inline
---

# Arrizabalaga 2015 Global habitat preferences of commercially valuable tuna
Spatial overlap~ life history traits+ temp+O2

Used six tuna species in the Pacific, Atlantic and Indian Oceans.
We may ask for the data.

Both quotient analysis and Generalised Additive Models were used to determine habitat preference with respect to eight biotic and abiotic variables

Quotient analysis embed environment quality into a new index Q. Abundance at a certain habitat can be transformed by embedding habitat quality. We can then use these Q to calculate index of overlapping 

      SP1     SP2 
T25   0.5      4
T26   1        2
T27   1.2      0.5
T28   3        0.1

The question becomes: how does fish preference on temperature depends on life history traits?

Intra-population spatial overlap index~ life history traits+ temp+ O2.

Life history traits such as mobility and changes in diet are traits which directly explain age-specific niche diffefentiation. And trait such as body size is likely associated with these above traits. 


# Note March 06
1. To identify index for intra-population spatial overlap
2. What is the hypothesis?
3. Other factors that influence intra-population spatial overlap (i.e. habitat heterogeneity, availability) 


# Procedure:
1. To quantify the degree of ontogenetic niche shift
2. To link it with life history traits

# Reference list (online)

# Cotan's ecology paper
https://esajournals.onlinelibrary.wiley.com/doi/full/10.1890/15-1270.1

## Spatial distribution
https://onlinelibrary.wiley.com/doi/full/10.1111/ele.13360
https://www.nature.com/articles/s41598-019-53998-2
http://janohlberger.com/Homepage/download/cline-nature-ee-2019%20(1).pdf

## Ontogenetic niche shift
https://link.springer.com/article/10.1007/s10021-013-9645-4  

## Age structure model in dispersive/residence contingent
Kerr 2010 https://esajournals.onlinelibrary.wiley.com/doi/abs/10.1890/08-1382.1

# R package "rfishbase"
```{r}
library("rfishbase")
library("dplyr")
fish <- c("Oreochromis niloticus", "Salmo trutta")
fish<-validate_names(c("Oreochromis niloticus", "Salmo trutta"))
fish
fish <- species_list(Genus = "Labroides")
fish
trout <- common_to_sci("trout")
trout
species(trout$Species)
dat <- species(trout$Species, fields=c("Species", "PriceCateg", "Vulnerability"))
dat
list_fields("Resilience")
stocks(trout$Species, fields=c("Species", "Resilience", "StockDefs"))

```

# Ideas
Differences in distribution between species depends on 
1. Ontogenetic-specific life history traits:
relative swimming behavior, changes in diet, 
*maximum body length* may correlates with all the above traits.

2. Environment:
landscape structure

3. Food availability


# Ecospat package
```{r}
install.packages("devtools")
library(devtools)
install_github(repo="ecospat/ecospat/ecospat")
library(ecospat)


```





